%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Sebastian Newberry} \\ \vspace{1pt}
    \small 248-444-7804 $|$ \href{mailto:snewbe@wayne.edu}{\underline{snewbe@wayne.edu}} $|$ 
    \href{https://linkedin.com/in/sebastian-newberry-288058191/}{\underline{linkedin.com/in/sebastian-newberry/}} $|$
    \href{https://github.com/SebastianNewberry}{\underline{github.com/SebastianNewberry}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Wayne State University}{Detroit, MI}
      {Bachelor of Science in Computer Science \textbar{} GPA: 3.97}{Aug. 2022 -- Dec. 2025}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Wayne State University}{Detroit, MI}
      {M.S. with a major in A.I. Software and Systems}{Jan. 2026 -- Dec. 2026}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Detroit Public Schools X Rocket Companies}{July -- Aug. 2023, 2024, 2025}
      {Tutor, \href{https://rocket-group-project-2024.vercel.app/}{\color{Blue}View Trivia Game Project}, \href{https://eventplanner-alpha.vercel.app/ }{\color{Blue}View Event Planner Project}}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Led a team of 5 students in a technology tutoring program funded by Rocket Companies.}
        \resumeItem{Taught students core cybersecurity principles such as authentication token security, password hashing, and secure user input handling during web development.}
        \resumeItem{Built an interactive WebSocket-based game to demonstrate real-time communication differences between WebSockets and traditional HTTP.}
        \resumeItem{Deployed a backend server on a DigitalOcean VPS using Docker for containerization.}
        
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Wayne State Cyber Defense Club}{Sep. 2022 -- Present}
      {Windows Active Directory, View Wayne State CTF \href{https://github.com/SebastianNewberry/WSUCTF2024}{\color{Blue}2024} and \href{https://github.com/SebastianNewberry/WSUCTF2025}{\color{Blue} 2025} challenges}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Hardened Windows Server 2012 in the Collegiate Cyber Defense Competition (CCDC) to defend against simulated cyberattacks.}
        \resumeItem{Identified and exploited common web vulnerabilities, including SQLi, LFI, XSS, SSRF, and CSRF on platforms
        such as HackTheBox and TryHackMe, while gaining expertise in their prevention techniques.}
        \resumeItem{Regularly participated in HackTheBox challenges to strengthen my CTF skills and refine my ability to identify and
        mitigate real-world vulnerabilities.}
        \resumeItem{Gained hands-on experience with Bash scripting, Linux command-line tools, and Windows PowerShell in working
        through challenges on the Hackthebox website.}
        \resumeItem{Developed and designed web exploitation, pwn, and forensics challenges for the Wayne State University CTF competition.}
        \resumeItem{Utilized tools like Wireshark for capturing network traffic, Ghidra for decompiling binaries, Burp Suite for web reconnaissance and exploitation.}
        \resumeItem{Deployed CTF challenges using Docker and CTFd to create isolated, reproducible environments.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\href{https://github.com/SebastianNewberry/Final_Project_Intro_LLM/blob/main/Report.pdf}{\color{Blue}\textbf{Report on RAG (Retrieval Augmented Generation)}} $|$ \emph{Python, PyTorch, LaTex}}{Feb. 2025 - Apr. 2025}
          \resumeItemListStart
            \resumeItem{Authored a comprehensive report on Retrieval-Augmented Generation (RAG), demonstrating how LLMs retrieve external documents to answer queries.}
            \resumeItem{Implemented a practical demo of RAG using the RAGatouille Python library. View the notebook \href{https://colab.research.google.com/github/SebastianNewberry/Final_Project_Intro_LLM/blob/main/langchain_ollama_rag.ipynb}{\color{Blue}\textbf{here}}.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://volunteer-opportunities.vercel.app/}{\color{Blue}\textbf{Volunteer Opportunities}} $|$ \emph{ReactJs, NextJs, AWS S3, Pusher Websockets, PostgreSQL}}{Sept. 2024 -- Dec. 2024}
          \resumeItemListStart
            \resumeItem{Collaborated with a team of 5 to build a platform connecting volunteers with organizations.}
            \resumeItem{Designed and implemented a messaging interface from scratch, enabling seamless real-time communication on the
 web platform using Pusher Websockets.}
            \resumeItem{Integrated Mapbox with the project to render listings on maps with relevant information.}
            \resumeItem{Configured Zustand to implement efficient pagination, enabling seamless data loading without the need for page
 refreshes.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://devpost.com/software/privatedelivery/}{\color{Blue}\textbf{MHacks 15 - Private Delivery}} $|$ \emph{ReactJs, NextJs, MySQL, Prisma}}{Feb. 2023}
          \resumeItemListStart
            \resumeItem{Developed a full-stack platform to match delivery requests with available drivers.}
            \resumeItem{Gained hands-on experience through collaborative development in a 24-hour online hackathon.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, TypeScript, C++, Java, R, MongoDB, SQL (PostgreSQL, MySQL), HTML/CSS} \\
     \textbf{Frameworks \& Libraries}{: Matplotlib, Node.js, NumPy, Pandas, PyTorch, React} \\
     \textbf{Developer Tools}{: Docker, Git} \\
     \textbf{Cloud Platforms}{: AWS (Amplify, Lambda, S3)}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}